DISTRIBUTED CROSS-RELATION-BASED FREQUENCY-DOMAIN\\ BLIND SYSTEM IDENTIFICATION USING ONLINE-ADMM

### 2022-05-06 tikz/topology_details.tex
waiting for simulation to finish

        \draw[-stealth,black, line width=1.2] (A) to[bend left=20] node[above, pos=0.5, sloped, scale=1]{\(\x_i, \{\phi_1,\ldots,\phi_i\}\)}  (B);

        \draw[stealth-,gray, line width=1.2] (A) to[bend right=20] node[below, pos=0.5, sloped,scale=1]{\((\wf_j)_i,(\uuf_j)_i,\{\phi_1,\ldots,\phi_M\}\)}  (B);

>>>>

        \draw[-stealth,black, line width=1.2] (A) to[bend left=20] node[above, pos=0.5, sloped, scale=1]{\(\x_i, \hf_i, \{\|\bar{\hf}_1\|^2,\ldots,\|\bar{\hf}_i\|^2\}\)}  (B);

        \draw[stealth-,gray, line width=1.2] (A) to[bend right=20] node[below, pos=0.5, sloped,scale=1]{\((\wf_j)_i,(\uuf_j)_i,\{\|\bar{\hf}_1\|^2,\ldots,\|\bar{\hf}_M\|^2\}\)}  (B);
